Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 Discussion.tex
spell check on body of paper

We refer to this modified version of
Algorithm~\ref{alg:basic-incentivizing} as the
\emph{Discrete-Preference Algorithm.}
We outline a proof of the following result for this algortithm under
Assumption~\ref{a:discrete} in Appendix~\ref{sec:discussion-proof1}.

@@

This knowledge of \MinProb allows the algorithm to incentivize
significantly fewer arm pulls.
We refer to this modified version of
Algorithm~\ref{alg:basic-incentivizing} as the \emph{Known-\MinProb
Algorithm.}
We outline a proof of the following result for this algortithm under
Assumption~\ref{a:known-p} in Appendix~\ref{sec:discussion-proof2}.

>>>>

We refer to this modified version of
Algorithm~\ref{alg:basic-incentivizing} as the
\emph{Discrete-Preference Algorithm.}
We outline a proof of the following result for this algorithm under
Assumption~\ref{a:discrete} in Appendix~\ref{sec:discussion-proof1}.

@@

This knowledge of \MinProb allows the algorithm to incentivize
significantly fewer arm pulls.
We refer to this modified version of
Algorithm~\ref{alg:basic-incentivizing} as the \emph{Known-\MinProb
Algorithm.}
We outline a proof of the following result for this algorithm under
Assumption~\ref{a:known-p} in Appendix~\ref{sec:discussion-proof2}.
